---
title: "Installing Package Dependencies"
output: 
  html_notebook:
    toc: true
    toc_depth: 2
    toc_float: true
editor_options: 
  chunk_output_type: inline
---


# Updating CRAN Mirror

Before we install the packages we'll need for this course, let's make sure we are pulling from a recent mirror of CRAN. By default MRS points to an old "snapshot" of CRAN, usually around the time that version of MRS was built, tested and released.

```{r update_repos}

r <- getOption("repos")
# set mirror to something a bit more recent
r["CRAN"] <- "https://mran.revolutionanalytics.com/snapshot/2017-08-15/"
options(repos = r)


```


# Install magrittr and ggplot2 

We'll install some familiar packages:

```{r gg_pipe}

pkgs_install <- c("tidyverse", "rmarkdown", "knitr")
install.packages(pkgs_install)

```


# Install curl and httr for devtools

We'll need a couple of packages that are not yet avaialable on CRAN, but are available as a development release on github. To do so, we'll use the `devtools::install_github` function.

```{r devtools_install}

dev_deps <- c("httr", "curl", "devtools")
install.packages(dev_deps)

```

# Install sparklyr packages 

Let's install `sparklyr`, `dplyrXdf` and `sparklyrgrpahs`. The version of `sparklyr` as of this writing is 0.7.0.9, which is the version we'll use.

```{r git_install}


# install.packages("sparklyr")
install.packages("plotly")

devtools::install_github("tidyverse/dplyr")
devtools::install_github("rstudio/sparklyr")
devtools::install_github("h2oai/rsparkling", ref = "master")
devtools::install_github("RevolutionAnalytics/dplyrXdf")
devtools::install_github("kevinykuo/sparklygraphs")

```

# Install h2o Sparkling Water


```{r h2o}
if ("package:h2o" %in% search()) { detach("package:h2o", unload=TRUE) }
if ("h2o" %in% rownames(installed.packages())) { remove.packages("h2o") }

pkgs <- c("methods","statmod","stats","graphics","RCurl","jsonlite","tools","utils")
for (pkg in pkgs) {
    if (! (pkg %in% rownames(installed.packages()))) { install.packages(pkg) }
}

## Check your needed h2o version
## https://github.com/h2oai/rsparkling#install-h2o
# rsparkling::h2o_release_table()

install.packages("h2o", type="source", repos=(c("http://h2o-release.s3.amazonaws.com/h2o/rel-ueno/2/R")))
# install.packages("h2o", 
                 # type = "source", 
                 # repos = "http://h2o-release.s3.amazonaws.com/h2o/rel-vajda/4/R")

# install.packages("rsparkling")
devtools::install_github("h2oai/rsparkling", ref = "master")
options(rsparkling.sparklingwater.version = "2.1.1")
```

