# Modeling with RxSpark

This section shows how to use the `RxSpark` compute context for modeling.

# Locate RevoShare dir

Every MRS installation on a HDFS environment creates a share directory on HDFS. By default, each user will have her own shared directory under the `/user/RevoShare/` file path.

```{r revoshare}

rxHadoopListFiles("/user/RevoShare/")
username <- system("whoami", intern = TRUE)
data_path <- file.path("/user/RevoShare", username)

```

# Saving the Spark DataFrame to CSV

The `RxSpark` and the Spark Compute contexts are completely distinct compute environments. In order to use the `rx` functions, we need to move the Spark DataFrame into a format that MRS can understand.

## Write Sample Taxi to RevoShare 

```{r save_csv}

library(sparklyr)
spark_write_csv(taxi_binary, 
                path = file.path(data_path, 'sampleTaxi'))


```

Shut down the `sparklyr` application:

```{r spark_disconnect}
spark_disconnect(sc)

```


## Remove SUCCESS dir

```{r remove_success}

rxHadoopListFiles(file.path(data_path, "sampleTaxi"))
file_to_delete <- file.path(data_path, 
                            "sampleTaxi", "_SUCCESS")
delete_command <- paste("fs -rm", file_to_delete)
rxHadoopCommand(delete_command)


```


# Create HDFS and Spark Contexts for Revo

Let's create the pointers to the file paths and HDFS to use the `RxSpark` compute context.

```{r hdfs_pointers}

myNameNode <- "default"
myPort <- 0
hdfsFS <- RxHdfsFileSystem(hostName = myNameNode, 
                           port = myPort)

taxi_text <- RxTextData(file.path(data_path,
                                  "sampleTaxi"),
                        fileSystem = hdfsFS)

taxi_xdf <- RxXdfData(file.path(data_path, "taxiXdf"),
                      fileSystem = hdfsFS)


```


# create RxSpark compute context

```{r rx_spark_context}


computeContext <- RxSpark(consoleOutput=TRUE,
                          nameNode=myNameNode,
                          port=myPort,
                          executorCores=6, 
                          executorMem = "14g", 
                          executorOverheadMem = "7g", 
                          persistentRun = TRUE, 
                          extraSparkConfig = "--conf spark.speculation=true")

rxSetComputeContext(computeContext)



```

## Import to XDF

Now we use our `rxImport` function to import the csv into an xdf.

```{r csv_import_xdf}


col_classes <- c('VendorID' = "factor",
                 'passenger_count' = "integer",
                 'trip_distance' = "numeric",
                 'RateCodeID' = "factor",
                 'store_and_fwd_flag' = "factor",
                 'payment_type' = "factor",
                 'fare_amount' = "numeric",
                 'tip_amount' = "numeric",
                 'tolls_amount' = "numeric",
                 'pickup_hour' = "factor",
                 'pickup_dow' = "factor", 
                 'dropoff_hour' = "factor",
                 'dropoff_dow' = "factor",
                 'pickup_nhood' = "factor",
                 'dropoff_nhood' = "factor",
                 'kSplits' = "factor",
                 'tip_pct' = "numeric",
                 'good_tip' = "factor")

rxImport(inData = taxi_text, taxi_xdf, overwrite = TRUE, colClasses = col_classes)
rxGetInfo(taxi_xdf, getVarInfo = TRUE)


```

## Simple EDA

```{r eda_trips}

tip_dist_df <- rxCube(tip_pct ~ pickup_hour + pickup_dow, 
                      data = taxi_xdf, returnDataFrame = TRUE)

library(ggplot2)
library(magrittr)

tip_dist_df %>% ggplot(aes(x = pickup_hour, y = pickup_dow, fill = tip_pct)) +
  geom_tile() + theme_minimal() + 
  scale_fill_continuous(label = scales::percent) +
  labs(x = "Pickup Hour", y = "Pickup Day of Week", fill = "Tip Percent",
      title = "Distribution of Tip Percents",
      subtitle = "Do Passengers Tip More in the AM?")

```


# Creating Linear Models

Let's predict tip_pct as a function of distance and neighborhoods. In order to ensure that the neighbhorhood columns are treated as categorical, we will first convert them to factors. `RevoScaleR` and the `RxSpark` compute context are more picky about factor types than base R models, since they utilize data that is chunked and stored in distributed file systems. 

```{r rx_factors}

system.time(linmod <- rxLinMod(tip_pct ~ pickup_nhood +  trip_distance, 
                               data = taxi_xdf, cube = TRUE))

system.time(linmod <- rxLinMod(tip_pct ~ pickup_nhood +  trip_distance, 
                               data = taxi_xdf, cube = TRUE))

```

Now let's try to train the model with an additional categorical variable. We will use the `cube = TRUE` argument, which partitions the data across each category of the `pickup_nhood` variable. This results in significant speedups.

```{r rx_lm}

system.time(linmod <- rxLinMod(tip_pct ~ pickup_nhood + pickup_hour + trip_distance, 
                               data = taxi_xdf, cube = TRUE))

```

## Creating Decision and Ensemble Trees


```{r}

system.time(dtree <- rxDTree(good_tip ~ trip_distance + passenger_count,
                                 data = taxi_xdf, method = "class"))

plot(RevoTreeView::createTreeView(dtree))

system.time(dforest <- rxDForest(good_tip ~ pickup_nhood + pickup_hour + trip_distance,
                                 data = taxi_xdf, method = "class"))


```

## Publish to AzureML

We can use the [`AzureML`](https://github.com/RevolutionAnalytics/AzureML) package to convert our trained model as an Azure API. You'll need to get your security credentials from [AzureML Studio](https://studio.azureml.net). Click on _Settings_, copy _Workspace ID_. Then click on _Authorization Tokens_ at the top header, and copy your _Primary Authorization Token_. 

```{r}
packageVersion("AzureML")
library(AzureML)
ws <- workspace(
  id = "----",
  auth = "------" 
)

head(datasets(ws))
AzureML::experiments(ws)
```

As of right now (March 2017), AzureML does not have `rx` functions from the `RevoScaleR` package. Therefore, we need to convert our `RevoScaleR` model into a model that GNU-R/MRO can understand. Fortunately, the `RevoScaleR` modeling functions have methods to convert `rx` models into CRAN equivalents:

```{r}

rpartModel <- as.rpart(dtree)

```

Now let's create a scoring function: 

```{r}

scoringFn <- function(testdata) {
 
  library(rpart)
  predict(rpartModel, newdata = testdata)[, 1]
  
}
```

and let's copy into a data.frame a portion of our training data to use as our schema:


```{r}

library(dplyr)
exampleDF <- head(taxi_xdf) %>% select(trip_distance, passenger_count)

```

Let's make sure our scoring function works locally first:

```{r}

scoringFn(exampleDF)

```


We're ready to operationalize our model:


```{r}

endpoint <- publishWebService(ws, 
                              fun = scoringFn,
                              name = "Taxi-tip-rpart",
                              inputSchema = exampleDF)

```

Let's try it out:


```{r}


scores <- consume(endpoint, exampleDF)
head(scores)
```

